---
title: "Exploratory Data Analysis"
description: |
  The site provides a collection of resources and summary reports containing statistics and other relevant information about the datasets.
site: distill::distill_website
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
kbl_table <- function(x) {
  kbl(x) %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
    kable_styling(full_width = TRUE)
}

library(fontawesome)
library(kableExtra)
library(DT)
library(tidyverse)
library(xaringanExtra)
xaringanExtra::use_panelset()

```

## Summary Reports

  * [Arctic Ocean Summary Report](https://aiqc-hub.github.io/arc-report/)
  * [Baltic Sea Summary Report](https://aiqc-hub.github.io/bal-report/)
  * [Mediterranean Sea Summary Report](https://aiqc-hub.github.io/med-report/)

---

## Exported Parquet Datasets

All six Parquet files have been uploaded to Zenodo under the following DOI:

  * **DOI**: [10.5281/zenodo.17619571](https://doi.org/10.5281/zenodo.17619571)

<br>

::: {.panelset}
::: {.panel}

### Arctic Ocean

```{r, t_data_resource_arc, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("AR", "GL", "CORA"),
                 `Filename` = c("netcdf_nrt_ar_2.parquet",
                               "netcdf_nrt_ar_gl_2.parquet",
                               "netcdf_cora_ar_2.parquet"),
                 Size = c("695.43 MB", "1.98 GB", "1.06 GB"),
                 `# Platforms` = c(190, 551, 736),
                 `# Profiles` = c(339751, 742809, 446321),
                 `# Observations` = c(87991564, 273695664, 127506287))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::

::: {.panel}

### Baltic Sea

```{r, t_data_resource_bal, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("BO", "GL", "CORA"),
                 `Filename` = c("netcdf_nrt_bo_2.parquet",
                               "netcdf_nrt_bo_gl_2.parquet",
                               "netcdf_cora_bo_2.parquet"),
                 Size = c("64.29 MB", "170.93 MB", "163.22 MB"),
                 `# Platforms` = c(753, 8, 900),
                 `# Profiles` = c(112962, 48080, 228053),
                 `# Observations` = c(9334806, 26436908, 19076635))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::

::: {.panel}

### Mediterranean Sea


```{r, t_data_resource_med, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("MO", "GL", "CORA"),
                 `Filename` = c("netcdf_nrt_mo_2.parquet",
                               "netcdf_nrt_mo_gl_2.parquet",
                               "netcdf_cora_mo_2.parquet"),
                 Size = c("1.91 MB", "1.20 GB", "216.39 MB"),
                 `# Platforms` = c(10, 187, 191),
                 `# Profiles` = c(1655, 434183, 85053),
                 `# Observations` = c(363495, 169154995, 26447548))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::
:::

---

## Original NetCDF Datasets

::: {.panelset}
::: {.panel}

### Arctic Ocean

#### Data ID

  * **AR** & **GL**: [cmems_obs-ins_arc_phybgcwav_mynrt_na_irr](https://doi.org/10.48670/moi-00031)
  * **CORA**: [cmems_obs-ins_glo_phy-temp-sal_my_cora_irr](https://data.marine.copernicus.eu/product/INSITU_GLO_PHY_TS_DISCRETE_MY_013_001)


#### Number of files

```{r, t_netcdf_arc, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("AR", "GL", "CORA"),
                 `# Files` = c(190, 551, 18123),
                 `# Files with Time QC` = c(190, 551, 18123),
                 `# Files with Position QC` = c(190, 551, 18123),
                 `# Files with PRES` = c(188, 347, 16723))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::

::: {.panel}

### Baltic Sea

#### Data ID

  * **BO** & **GL**: [cmems_obs-ins_bal_phybgcwav_mynrt_na_irr](https://doi.org/10.48670/moi-00032)
  * **CORA**: [cmems_obs-ins_glo_phy-temp-sal_my_cora_irr](https://data.marine.copernicus.eu/product/INSITU_GLO_PHY_TS_DISCRETE_MY_013_001)
 

#### Number of files
  
```{r, t_netcdf_bal, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("BO", "GL", "CORA"),
                 `# Files` = c(753, 8, 11978),
                 `# Files with Time QC` = c(753, 8, 11978),
                 `# Files with Position QC` = c(461, 8, 11978),
                 `# Files with PRES` = c(576, 8, 11971))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::

::: {.panel}

### Mediterranean Sea

#### Data ID

  * **MO** & **GL**: [cmems_obs-ins_med_phybgcwav_mynrt_na_irr](https://doi.org/10.48670/moi-00044)
  * **CORA**: [cmems_obs-ins_glo_phy-temp-sal_my_cora_irr](https://data.marine.copernicus.eu/product/INSITU_GLO_PHY_TS_DISCRETE_MY_013_001)


#### Number of files

```{r, t_netcdf_med, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("MO", "GL", "CORA"),
                 `# Files` = c(79, 187, 7424),
                 `# Files with Time QC` = c(79, 187, 7424),
                 `# Files with Position QC` = c(79, 186, 7424),
                 `# Files with PRES` = c(79, 114, 7363))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::
:::

---

