### Detection criteria

::: {.panelset}
::: {.panel}

#### Duplicate profiles within platforms

The following variables must match:

 - Platform (`platform_code`)
 - Timestamp (`profile_timestamp`)
 - Rounded longitude (`round(longitude, 3)`)
 - Rounded latitude (`round(latitude, 3)`)

:::

::: {.panel}

#### Duplicate profiles across platforms

The following variables must match:

 - Timestamp (`profile_timestamp`)
 - Rounded longitude (`round(longitude, 3)`)
 - Rounded latitude (`round(latitude, 3)`)

The following variable must unmatch:

 - Platform (`platform_code`)

:::
:::

### Number of duplicate profiles

::: {.panelset}
::: {.panel}

#### Arctic Ocean

```{r, t_duplicate_arc, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("AR", "GL", "CORA"),
                 `# Profiles` = c(297876, 207372, 437619),
                 `# Within platforms` = c(0,  6572, 9796),
                 `Within (%)` = c("0%", "3.2%", "2.2%"),
                 `# Across platforms` = c(4080, 7249, 50465),
                 `Across (%)` = c("1.4%", "3.5%", "11.5%"))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::

::: {.panel}

#### Baltic Sea

```{r, t_duplicate_bal, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("BO", "GL", "CORA"),
                 `# Profiles` = c(107063, 6699, 215617),
                 `# Within platforms` = c(0, 234, 10617),
                 `Within (%)` = c("0%", "3.5%", "4.9%"),
                 `# Across platforms` = c(5845, 0, 50224),
                 `Across (%)` = c("5.5%", "0%", "23.3%"))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::

::: {.panel}

#### Mediterranean Sea

```{r, t_duplicate_med, echo = FALSE, message = FALSE, warning = FALSE}

df_tbl <- tibble(`Code` = c("MO", "GL", "CORA"),
                 `# Profiles` = c(1633, 96728, 82997),
                 `# Within platforms` = c(3, 14413, 13950),
                 `Within (%)` = c("0.2%", "14.9%", "16.8%"),
                 `# Across platforms` = c(0, 2326, 4226),
                 `Across (%)` = c("0%", "2.4%", "5.1%"))

kbl_table(df_tbl) %>% kable_styling(font_size = 12)

```

:::
:::
